Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-17 content/appendix.tex
.

    The fact that $\mpd(r)\ne\top_T$ means that there exists a realizable path corresponding to the fact $d$ along path $p$, and, by definition, $d$ must be contained in $M_F(p)(\varnothing)$.\mtodo{Is this hand-wavy?}
\end{proof}

>>>>

    The fact that $\mpd(r)\ne\top_T$ means that there exists a realizable path corresponding to the fact $d$ along path $p$, and, by definition, $d$ must be contained in $M_F(p)(\varnothing)$.
    %\mtodo{Is this hand-wavy?}
    %\otodo{No, I think it's fine.}
\end{proof}
